SDM\_the\_search\_for\_powers\_of\_2\_everywhere

### 2018-04-26 Chapters/Chapter01.tex
Minor Hathor improvements.

Bitcoin provides interesting incentives to all players, users and miners. On the one hand, users may have incentives to use Bitcoin because (i) the fees are small and does not depend on the amount being transfered --- but only in the size (in bytes) of the transaction ---; (ii) the transfers will be confirmed in a well-known period; (iii) it is not possible to revert an already confirmed transfer, not even with a judicial order; and (iv) and the currency issuance rate is well-known and preset in Bitcoin's rules, which makes Bitcoin's supply predictable and trustworthy, different from fiat currencies which depends on decisions of their central banks --- i.e., it would be virtually impossible to face a hyper inflation in Bitcoin due to currency issuance. On the other hand, miners have incentive to mine Bitcoin because new Bitcoins are found every ten minutes, and they may also collect the fees of unconfirmed transactions. These incentives have kept the Bitcoin network up and running since 2009 with barely any interruptions (99.99\% uptime).

@@

Bitcoin seems to have the most decentralized network between the cryptocurrencies, even so, there are few miners and mining pools which together control over 50\% of the network’s computing (hash)power. Thus, they have an oversized influence when it comes to changes in the Bitcoin protocol's behavior, and it is also seen as a problem to be solved. The more decentralized, the more trustworthy Bitcoin is.

>>>>

Bitcoin provides interesting incentives to all players, users and miners. On the one hand, users may have incentives to use Bitcoin because (i) the fees are small and does not depend on the amount being transfered --- but only in the size (in bytes) of the transaction ---; (ii) the transfers will be confirmed in a well-known period; (iii) it is not possible to revert an already confirmed transfer, not even with a judicial order; and (iv) and the currency issuance rate is well-known and preset in Bitcoin's rules, which makes Bitcoin's supply predictable and trustworthy, different from fiat currencies which depends on decisions of their central banks --- i.e., it would be virtually impossible to face a hyper inflation in Bitcoin due to currency issuance. On the other hand, miners have incentive to mine Bitcoin because new Bitcoins are found every ten minutes, and they may also collect the fees of unconfirmed transactions. It is important to highlight that anyone can become a miner, and there is no entry cost besides the mining equipment. These incentives have kept the Bitcoin network up and running since 2009 with barely any interruptions (99.99\% uptime). For further information about incentives, see \citet{ma2018market, catalini2016some}.

@@

Bitcoin seems to have the most decentralized network between the cryptocurrencies, even so, there are few miners and mining pools which together control over 50\% of the network’s computing (hash)power (see \citet{gencer2018decentralization}). Thus, they have an oversized influence when it comes to changes in the Bitcoin protocol's behavior, and it is also seen as a problem to be solved. The more decentralized, the more trustworthy Bitcoin is.
